\begin{thebibliography}{99}

\bibitem{Marples1993}
Marples B, Joiner MC.
\textit{The response of Chinese hamster V79 cells to low radiation doses: evidence of enhanced sensitivity of the whole cell population.}
Radiat Res. 1993;133(1):41-51.

\bibitem{Polgar2022}
Polgár S, Schofield PN, Madas BG.
\textit{Datasets of in vitro clonogenic assays showing low dose hyper-radiosensitivity and induced radioresistance.}
Sci Data. 2022;9:555.

\bibitem{Joiner2001}
Joiner MC, Marples B, Lambin P, Short SC, Turesson I.
\textit{Low-dose hypersensitivity: current status and possible mechanisms.}
Int J Radiat Oncol Biol Phys. 2001;49(2):379-389.

\bibitem{MarplesCollis2008}
Marples B, Collis SJ.
\textit{Low-dose hyper-radiosensitivity: past, present, and future.}
Int J Radiat Oncol Biol Phys. 2008;70(5):1310-1318.

\bibitem{Wouters1996}
Wouters BG, Skarsgard LD.
\textit{Low-dose hypersensitivity and increased radioresistance in a panel of human tumor cell lines with different radiosensitivity.}
Radiat Res. 1996;146(4):399-413.

\bibitem{Marples1997}
Marples B, Lambin P, Skov KA, Joiner MC.
\textit{Low dose hyper-radiosensitivity and increased radioresistance in mammalian cells.}
Int J Radiat Biol. 1997;71(6):721-735.

\bibitem{Short2003}
Short SC, Woodcock M, Marples B, Joiner MC.
\textit{Effects of cell cycle phase on low-dose hyper-radiosensitivity.}
Int J Radiat Biol. 2003;79(2):99-105.

\bibitem{Krueger2007}
Krueger SA, Collis SJ, Joiner MC, Wilson GD, Marples B.
\textit{Transition in survival from low-dose hyper-radiosensitivity to increased radioresistance is independent of activation of ATM Ser1981 activity.}
Int J Radiat Oncol Biol Phys. 2007;69(4):1262-1271.

\bibitem{Skov1994}
Skov K, Marples B, Matthews JB, Joiner MC, Zhou H.
\textit{A preliminary investigation into the extent of increased radioresistance or hyper-radiosensitivity in cells of hamster cell lines known to be deficient in DNA repair.}
Radiat Res. 1994;138(1 Suppl):S126-S129.

\bibitem{Xue2016}
Xue J, Zong Y, Li PD, et al.
\textit{Low-dose hyper-radiosensitivity in human hepatocellular HepG2 cells is associated with Cdc25C-mediated G2/M cell cycle checkpoint control.}
Int J Radiat Biol. 2016;92(10):543-547.

\bibitem{Dai2009}
Dai X, Tao D, Wu H, et al.
\textit{Low dose hyper-radiosensitivity in human lung cancer cell line A549 and its possible mechanisms.}
J Huazhong Univ Sci Technol Med Sci. 2009;29(1):101-106.

\bibitem{Short1999}
Short SC, Mitchell SA, Boulton P, Woodcock M, Joiner MC.
\textit{The response of human glioma cell lines to low-dose radiation exposure.}
Int J Radiat Biol. 1999;75(11):1341-1348.

\bibitem{Lambin1994}
Lambin P, Marples B, Fertil B, Malaise EP, Joiner MC.
\textit{Hypersensitivity of a human tumour cell line to very low radiation doses.}
Int J Radiat Biol. 1994;63(5):639-650.

\bibitem{Lambin1996}
Lambin P, Fertil B, Malaise EP, Joiner MC.
\textit{Multiphasic survival curves for cells of human tumor cell lines: induced repair or hypersensitive subpopulation?}
Radiat Res. 1996;138(1 Suppl):S32-S36.

\bibitem{Wouters1997}
Wouters BG, Skarsgard LD.
\textit{The response of a human tumor cell line to low radiation doses: evidence of enhanced sensitivity.}
Radiat Res. 1997;138(1 Suppl):S76-S80.

\bibitem{Rothkamm2003}
Rothkamm K, Löbrich M.
\textit{Evidence for a lack of DNA double-strand break repair in human cells exposed to very low x-ray doses.}
Proc Natl Acad Sci USA. 2003;100(9):5057-5062.

\bibitem{Martin2013}
Martin LM, Marples B, Coffey M, et al.
\textit{DNA mismatch repair and the DNA damage response to ionizing radiation: making sense of apparently conflicting data.}
Cancer Treat Rev. 2013;39(8):S34-S42.

\bibitem{Hermann2008}
Hermann RM, Christiansen H, Germer CT, et al.
\textit{Low-dose hyper-radiosensitivity in prostate cancer cell lines.}
Strahlenther Onkol. 2008;184(3):168-173.

\bibitem{Ryan2009}
Ryan LA, Wilkins RC, McFarlane NM, et al.
\textit{Relative biological effectiveness of 280 keV neutrons for apoptosis in human lymphocytes.}
Health Phys. 2009;96(1):39-47.

\bibitem{AlMayah2022}
Al-Mayah A, Irons SL, Mothersill C, Kadhim M.
\textit{Genomic instability in non-targeted human cells.}
Mutat Res. 2022;823:111756.

\bibitem{Guirado2012}
Guirado D, Ruiz-Arrebola S, Sánchez-Reyes A.
\textit{Low-dose radiation hyper-radiosensitivity in multicellular tumour spheroids.}
Br J Radiol. 2012;85(1018):e1155-e1162.

\bibitem{Hanu2017}
Hanu AM, Patel DJ.
\textit{Low-dose hyper-radiosensitivity in esophageal adenocarcinoma.}
Int J Radiat Oncol Biol Phys. 2017;99(2):E573.

\bibitem{Andaur2018}
Andaur R, Morales D, Fernández M.
\textit{Low-dose hyper-radiosensitivity in colorectal cancer cells: role of DNA damage response.}
Radiat Oncol. 2018;13:89.

\bibitem{Marples1996}
Marples B, Adomat H, Koch CJ, Skov KA.
\textit{Response of V79 cells to low doses of X-rays and negative pi-mesons: clonogenic survival and DNA strand breaks.}
Int J Radiat Biol. 1996;70(4):429-436.

\bibitem{Koval1984}
Koval TM.
\textit{Multiphasic survival response of a radioresistant lepidopteran insect cell line.}
Radiat Res. 1984;98(3):642-648.

\end{thebibliography}
