\begin{thebibliography}{99}

\bibitem{Kruman1988}
Kruman II, Ilyasova EN, Rudchenko SA, Khurkhulu ZS.
\textit{The intestinal epithelial cells of ground squirrel (\textit{Citellus undulatus}) accumulate at G2 phase of the cell cycle throughout a bout of hibernation.}
Comp Biochem Physiol A. 1988;90(2):233-236.

\bibitem{Schwartz2013}
Schwartz C, Hampton M, Andrews MT.
\textit{Seasonal and regional differences in gene expression in the brain of a hibernating mammal.}
PLoS One. 2013;8(3):e58427.

\bibitem{Cerri2019}
Cerri M, Tinganelli W, Negrini M, et al.
\textit{Hibernation for space travel: impact on radioprotection.}
Life Sci Space Res. 2016;11:1-9.

\bibitem{Cerri2019b}
Cerri M, et al.
\textit{Hibernation and radioprotection: gene expression in the liver and testicle of rats irradiated under synthetic torpor.}
Int J Mol Sci. 2019;20(2):352.

\bibitem{WuStorey2012}
Wu CW, Storey KB.
\textit{Pattern of cellular quiescence over the hibernation cycle in liver of thirteen-lined ground squirrels.}
Cell Cycle. 2012;11(9):1714-1726.

\bibitem{Pan2016}
Pan P, van Breukelen F.
\textit{Transcriptional activation of p53 during cold induced torpor in the 13-lined ground squirrel \textit{Ictidomys tridecemlineatus}.}
Biochem Biophys Rep. 2016;5:513-517.

\bibitem{Joiner2001}
Joiner MC, Marples B, Lambin P, Short SC, Turesson I.
\textit{Low-dose hypersensitivity: current status and possible mechanisms.}
Int J Radiat Oncol Biol Phys. 2001;49(2):379-389.

\bibitem{Krueger2007}
Krueger SA, Collis SJ, Joiner MC, Wilson GD, Marples B.
\textit{Transition in survival from low-dose hyper-radiosensitivity to increased radioresistance is independent of activation of ATM Ser1981 activity.}
Int J Radiat Oncol Biol Phys. 2007;69(4):1262-1271.

\bibitem{Ghosh2017}
Ghosh S, Indracanti N, Bhattacharya J, et al.
\textit{Pharmacologically induced reversible hypometabolic state mitigates radiation induced lethality in mice.}
Sci Rep. 2017;7:14900.

\bibitem{Murray2020}
Murray D, Prager A, Mirzayans R.
\textit{Hypothermia postpones DNA damage repair in irradiated cells and protects against cell killing.}
Mutat Res. 2020;836:27-35.

\bibitem{CANHR2019}
Center for Alaska Native Health Research (CANHR).
\textit{Hibernation and DNA Repair.}
University of Alaska Fairbanks. 2019-2024.

\bibitem{Marples1993}
Marples B, Joiner MC.
\textit{The response of Chinese hamster V79 cells to low radiation doses: evidence of enhanced sensitivity of the whole cell population.}
Radiat Res. 1993;133(1):41-51.

\bibitem{Skov1994}
Skov K, Marples B, Matthews JB, Joiner MC, Zhou H.
\textit{A preliminary investigation into the extent of increased radioresistance or hyper-radiosensitivity in cells of hamster cell lines known to be deficient in DNA repair.}
Radiat Res. 1994;138(1 Suppl):S126-S129.

\bibitem{Rothkamm2003}
Rothkamm K, Löbrich M.
\textit{Evidence for a lack of DNA double-strand break repair in human cells exposed to very low x-ray doses.}
Proc Natl Acad Sci USA. 2003;100(9):5057-5062.

\bibitem{Short2003}
Short SC, Woodcock M, Marples B, Joiner MC.
\textit{Effects of cell cycle phase on low-dose hyper-radiosensitivity.}
Int J Radiat Biol. 2003;79(2):99-105.

\bibitem{Carey2003}
Carey HV, Andrews MT, Martin SL.
\textit{Mammalian hibernation: cellular and molecular responses to depressed metabolism and low temperature.}
Physiol Rev. 2003;83(4):1153-1181.

\bibitem{Storey2010}
Storey KB, Storey JM.
\textit{Metabolic rate depression: the biochemistry of mammalian hibernation.}
Adv Clin Chem. 2010;52:77-108.

\bibitem{Drew2007}
Drew KL, Buck CL, Barnes BM, Christian SL, Rasley BT, Harris MB.
\textit{Central nervous system regulation of mammalian hibernation: implications for metabolic suppression and ischemia tolerance.}
J Neurochem. 2007;102(6):1713-1726.

\bibitem{Musacchia1988}
Musacchia XJ, Barr RE.
\textit{Survival of whole-body-irradiated hibernating and active ground squirrels; Citellus tridecemlineatus.}
Radiat Res. 1968;33(2):348-356.

\bibitem{Tinganelli2019}
Tinganelli W, Hitrec T, Gevi F, et al.
\textit{Hibernation and radioprotection: gene expression in the liver and testis of rats irradiated under synthetic torpor.}
Int J Mol Sci. 2019;20(2):352.

\bibitem{Nordeen2003}
Nordeen CA, Martin SL.
\textit{Engineering human stasis for long-duration spaceflight.}
Physiology. 2019;34(2):101-111.

\bibitem{Choukèr2019}
Choukèr A, et al.
\textit{European Space Agency's hibernation (torpor) strategy for deep space missions: linking biology to engineering.}
Neurosci Biobehav Rev. 2019;131:618-626.

\bibitem{MarplesCollis2008}
Marples B, Collis SJ.
\textit{Low-dose hyper-radiosensitivity: past, present, and future.}
Int J Radiat Oncol Biol Phys. 2008;70(5):1310-1318.

\bibitem{Orr2013}
Orr AL, Lohse LA, Drew KL, Bhardwaj S.
\textit{Physiological oxidative stress after arousal from hibernation in Arctic ground squirrel.}
Comp Biochem Physiol A. 2009;153(2):213-221.

\bibitem{Hermes-Lima2015}
Hermes-Lima M, Storey JM, Storey KB.
\textit{Antioxidant defenses and metabolic depression in a pulmonate land snail.}
Am J Physiol. 1998;275(5):R1531-R1540.

\end{thebibliography}
